---
title: "MoFA Nepal Remittance Corridor Pipeline"
subtitle: "Measuring the Invisible -- Korea Corridor, Gulf Comparators, and EPS MOU Analysis"
author: "Sambhav Lamichhane"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
    number_sections: true
    fig_crop: false
    highlight: null
    includes:
      in_header: tex/preamble.tex
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \floatplacement{figure}{H}
geometry: margin=1in
fontsize: 11pt
params:
  use_real_data: true
  run_nrb_pdf_densification: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, message = FALSE, warning = FALSE,
  fig.align = "center", fig.width = 7, fig.height = 4.5,
  dpi = 200, out.width = "100%"
)

if (!file.exists("run_all.R")) {
  if (file.exists("mofa_r_pipeline/run_all.R")) setwd("mofa_r_pipeline")
  else stop("Set working directory to mofa_r_pipeline/ before rendering.")
}

tex_root <- normalizePath("tex/latex", mustWork = FALSE)
if (dir.exists(tex_root)) {
  tex_paths <- list.dirs(tex_root, recursive = FALSE, full.names = TRUE)
  Sys.setenv(TEXINPUTS = paste0(paste(c(tex_paths, tex_root), collapse = "//:"), "//:"))
}

required_pkgs <- c(
  "dplyr", "tidyr", "ggplot2", "readxl", "stringr",
  "plm", "lmtest", "sandwich", "broom",
  "zoo", "strucchange", "tseries", "forecast",
  "knitr", "pdftools", "rmarkdown"
)
missing <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing) > 0) install.packages(missing, repos = "https://cloud.r-project.org")
invisible(lapply(required_pkgs, library, character.only = TRUE))

dir.create("output/figures", recursive = TRUE, showWarnings = FALSE)
dir.create("output/tables",  recursive = TRUE, showWarnings = FALSE)

USE_REAL_DATA <- params$use_real_data
RUN_NRB_PDF   <- params$run_nrb_pdf_densification

kable_pdf <- function(x, caption = NULL) {
  knitr::kable(x, format = "latex", booktabs = TRUE, caption = caption, longtable = FALSE)
}

show_table <- function(path, caption = NULL, digits = 2, max_rows = 40L) {
  if (!file.exists(path)) {
    return(kable_pdf(data.frame(note = paste("Not found:", path)), caption))
  }
  df <- read.csv(path, stringsAsFactors = FALSE)
  if (nrow(df) > max_rows) df <- df[seq_len(max_rows), , drop = FALSE]
  num_cols <- vapply(df, is.numeric, logical(1))
  if (any(num_cols)) df[num_cols] <- lapply(df[num_cols], round, digits)
  kable_pdf(df, caption)
}

show_fig <- function(path) {
  if (!file.exists(path)) { plot.new(); text(0.5, 0.5, paste("Missing:", path)); return() }
  knitr::include_graphics(path)
}

source_script <- function(path) {
  cat("\n", strrep("=", 60), "\n", path, "\n", strrep("=", 60), "\n", sep = "")
  source(path, local = FALSE)
}
```

# Introduction

This report runs the full MoFA Cluster 10 remittance pipeline and embeds key outputs.

**PDF prerequisites:** install `tinytex` and run `tinytex::install_tinytex()`. For NRB PDF densification, install poppler (`brew install poppler` on macOS).

**Render:** RStudio Knit to PDF, or `rmarkdown::render("mofa_pipeline_report.Rmd")` from the project folder.

Set `params$use_real_data: false` in the YAML header to use demo data instead of collected real files.

# Part 1 -- Data preparation

## RPW corridor panel

```{r data-prep-rpw, cache=TRUE}
if (USE_REAL_DATA) {
  source_script("scripts/00b_reshape_rpw_excel.R")
} else {
  source_script("scripts/00_generate_demo_data.R")
}
```

```{r rpw-head}
rpw_file <- if (USE_REAL_DATA) "data/raw/rpw_real.csv" else "data/raw/rpw_demo.csv"
kable_pdf(head(read.csv(rpw_file, stringsAsFactors = FALSE), 8),
          caption = "RPW panel (first rows)")
```

## Korea operator fees

```{r data-prep-korea, cache=TRUE}
if (USE_REAL_DATA) {
  source_script("scripts/00d_ingest_korea_fees_real.R")
}
```

```{r korea-fees-table}
if (USE_REAL_DATA && file.exists("data/raw/korea_mto_fees_real.csv")) {
  fees <- read.csv("data/raw/korea_mto_fees_real.csv", stringsAsFactors = FALSE)
  if ("notes" %in% names(fees)) fees$notes <- NULL
  kable_pdf(fees, caption = "Korea operator fees")
}
```

## NRB monthly series

```{r data-prep-nrb, cache=TRUE, eval=RUN_NRB_PDF}
if (USE_REAL_DATA) {
  source_script("scripts/00c_ingest_nrb_real.R")
}
```

```{r nrb-summary}
if (USE_REAL_DATA && file.exists("data/raw/nrb_remit_monthly_real.csv")) {
  nrb <- read.csv("data/raw/nrb_remit_monthly_real.csv", stringsAsFactors = FALSE)
  nrb$month <- as.Date(nrb$month)
  cat("Months:", nrow(nrb), "| Range:", format(min(nrb$month), "%Y-%m"), "-",
      format(max(nrb$month), "%Y-%m"), "\n")
  cols <- c("month", "remit_npr_bn", "fx_reserve_usd_bn", "labor_permits_new", "source")
  kable_pdf(nrb[, cols, drop = FALSE])
}
```

# Part 2 -- Load and clean RPW

```{r load-rpw, cache=TRUE}
source_script("scripts/01_load_clean_rpw.R")
```

# Part 3 -- Gulf corridor diagnostics

```{r corridor-diagnostics, cache=TRUE}
source_script("scripts/02_corridor_diagnostics.R")
```

```{r table1}
show_table("output/tables/table1_nepal_corridor_diagnostic.csv", "Nepal corridor diagnostic")
```

```{r table2}
show_table("output/tables/table2_country_comparison.csv", "Cross-country comparison")
```

```{r fig1, fig.cap="Nepal corridor cost trend"}
show_fig("output/figures/fig1_nepal_cost_trend.png")
```

```{r fig2, fig.cap="Fee vs FX margin decomposition"}
show_fig("output/figures/fig2_fee_vs_fx_decomposition.png")
```

# Part 4 -- Korea cost reconstruction

```{r korea-reconstruction, cache=TRUE}
source_script("scripts/02b_korea_cost_reconstruction.R")
```

```{r korea-comparison}
show_table("output/tables/table_korea_vs_gulf_comparison.csv", "Korea vs Gulf MTO costs")
```

```{r fig-korea, fig.cap="Korea operator costs (KRW 500,000)"}
show_fig("output/figures/fig_korea_operator_costs.png")
```

# Part 5 -- Panel regression

```{r panel-regression, cache=TRUE}
source_script("scripts/03_panel_regression.R")
```

```{r table3a}
show_table("output/tables/table3a_model_within_nepal.csv", "Model A: within Nepal")
```

```{r table3b}
show_table("output/tables/table3b_model_cross_country.csv", "Model B: cross-country")
```

# Part 6 -- NRB time series

```{r timeseries, cache=TRUE}
source_script("scripts/04_timeseries_structural_break.R")
```

```{r table4}
show_table("output/tables/table4_chow_test_summary.csv", "Chow test summary")
```

```{r fig3, fig.cap="STL decomposition"}
show_fig("output/figures/fig3_stl_decomposition.png")
```

```{r fig4, fig.cap="Structural breaks"}
show_fig("output/figures/fig4_structural_breaks.png")
```

# Part 7 -- Monte Carlo

```{r monte-carlo, cache=TRUE}
source_script("scripts/05_monte_carlo_retention.R")
```

```{r table5}
show_table("output/tables/table5_monte_carlo_summary.csv", "Monte Carlo summary", max_rows = 20)
```

All figures in USD million/year. Scenario 1 = FX flows recaptured into formal channels if informal share falls from ~55% to ~20%. Scenario 2 = household savings if Saudi bank-channel users switch to MTOs.

```{r fig5, fig.cap="Monte Carlo distributions"}
show_fig("output/figures/fig5_monte_carlo_distributions.png")
```

# Part 8 -- EPS MOU analysis

```{r eps-mou, cache=TRUE}
source_script("scripts/06_eps_mou_analysis.R")
```

```{r table6a}
show_table("output/tables/table6a_eps_mou_clause_mapping.csv", "EPS MOU clauses")
```

```{r table6b}
show_table("output/tables/table6b_instrument_comparison.csv", "Comparator instruments")
```

```{r fig6, fig.cap="EPS gap matrix"}
show_fig("output/figures/fig6_eps_gap_matrix.png")
```


# Appendix -- Proposed EPS clause

```{r eps-clause, results='asis'}
p <- "output/tables/table6c_proposed_eps_clause.txt"
if (file.exists(p)) cat(readLines(p), sep = "\n")
```

# Appendix -- Output inventory

```{r output-inventory}
inv <- function(d) {
  if (!dir.exists(d)) return(NULL)
  f <- list.files(d)
  data.frame(file = f, kb = round(file.info(file.path(d, f))$size / 1024, 1))
}
kable_pdf(inv("output/figures"), caption = "Figures produced")
kable_pdf(inv("output/tables"), caption = "Tables produced")
```
